\begin{thebibliography}{}

\bibitem[Gebser et~al., 2019]{PotasscoUserGuide19}
Gebser, M., Kaminski, R., Kaufmann, B., Lindauer, M., Ostrowski, M., Romero, J., Schaub, T., and Thiele, S. (2019).
\newblock {\em Potassco User Guide}, 2.2.0.

\bibitem[Gebser et~al., 2018a]{geobotscsangso18a}
Gebser, M., Obermeier, P., Otto, T., Schaub, T., Sabuncu, O., Nguyen, V., and Son, T. (2018a).
\newblock Experimenting with robotic intra-logistics domains.
\newblock {\em Theory and Practice of Logic Programming}, 18(3-4):502--519.

\bibitem[Gebser et~al., 2018b]{geobscra18a}
Gebser, M., Obermeier, P., Schaub, T., Ratsch{-}Heitmann, M., and Runge, M. (2018b).
\newblock Routing driverless transport vehicles in car assembly with answer set programming.
\newblock {\em Theory and Practice of Logic Programming}, 18(3-4):520--534.

\bibitem[G{\'{o}}mez et~al., 2021]{DBLP:journals/access/GomezHB21}
G{\'{o}}mez, R.~N., Hern{\'{a}}ndez, C., and Baier, J.~A. (2021).
\newblock A compact answer set programming encoding of multi-agent pathfinding.
\newblock {\em {IEEE} Access}, 9:26886--26901.

\bibitem[H{\"{a}}cker et~al., 2021]{distant}
H{\"{a}}cker, C., Bouros, P., Chondrogiannis, T., and Althaus, E. (2021).
\newblock Most diverse near-shortest paths.
\newblock In
% Meng, X., Wang, F., Lu, C., Huang, Y., Shekhar, S., and Xie, X., editors,
{\em 29th International Conference on Advances in Geographic Information Systems},
pages 229--239. {ACM}.

\bibitem[Hanaka et~al., 2021]{diverse}
Hanaka, T., Kobayashi, Y., Kurita, K., Lee, S.~W., and Otachi, Y. (2021).
\newblock Computing diverse shortest paths efficiently: {A} theoretical and experimental study.
\newblock {\em CoRR}, abs/2112.05403.

\bibitem[Hus{\'{a}}r et~al., 2022]{AAMAS_corridors}
Hus{\'{a}}r, M., Svancara, J., Obermeier, P., Bart{\'{a}}k, R., and Schaub, T.  (2022).
\newblock Reduction-based solving of multi-agent pathfinding on large maps using graph pruning.
\newblock In
% Faliszewski, P., Mascardi, V., Pelachaud, C., and Taylor, M.~E., editors,
{\em 21st International Conference on Autonomous Agents and Multiagent Systems},
pages 624--632.
IFAAMAS. % International Foundation for Autonomous Agents and Multiagent Systems.

\bibitem[Kaminski et~al., 2020]{karoscwa20a}
Kaminski, R., Romero, J., Schaub, T., and Wanko, P. (2022).
\newblock How to build your own ASP-based system?!
\newblock {\em Theory and Practice of Logic Programming}, 23(1):299-361.

\bibitem[Kornhauser et~al., 1984]{pebble_motion}
Kornhauser, D., Miller, G.~L., and Spirakis, P.~G. (1984).
\newblock Coordinating pebble motion on graphs, the diameter of permutation groups, and applications.
\newblock In {\em 25th Annual Symposium on Foundations of Computer Science}, pages 241--250.

\bibitem[Li et~al., 2020]{sven_lifelong}
Li, J., Tinka, A., Kiesel, S., Durham, J.~W., Kumar, T. K.~S., and Koenig, S. (2020).
\newblock Lifelong multi-agent path finding in large-scale warehouses.
\newblock In
% Seghrouchni, A. E.~F., Sukthankar, G., An, B., and Yorke{-}Smith, N., editors,
{\em 19th International Conference on Autonomous Agents and Multiagent Systems},
pages 1898--1900.
IFAAMAS. % International Foundation for Autonomous Agents and Multiagent Systems.

\bibitem[Nguyen et~al., 2017]{ngobsoscye17a}
Nguyen, V., Obermeier, P., Son, T.~C., Schaub, T., and Yeoh, W. (2017).
\newblock Generalized target assignment and path finding using answer set programming.
\newblock In
% Sierra, C., editor,
{\em 26th International Joint Conference on Artificial Intelligence},
pages 1216--1223. ijcai.org.

\bibitem[Ratner and Warmuth, 1990]{NP-hard1}
Ratner, D. and Warmuth, M.~K. (1990).
\newblock NxN puzzle and related relocation problem.
\newblock {\em J. Symb. Comput.}, 10(2):111--138.

\bibitem[Sharon et~al., 2011]{ICTS_soc}
Sharon, G., Stern, R., Goldenberg, M., and Felner, A. (2011).
\newblock The increasing cost tree search for optimal multi-agent pathfinding.
\newblock In {\em 22nd International Joint Conference on Artificial Intelligence},
pages 662--667.

\bibitem[Silver, 2005]{DBLP:conf/aiide/Silver05}
Silver, D. (2005).
\newblock Cooperative pathfinding.
\newblock In {\em Artificial Intelligence and Interactive Digital Entertainment},
pages 117--122.

\bibitem[Stern et~al., 2019]{stern2019mapfVarians}
Stern, R., Sturtevant, N.~R., Felner, A., Koenig, S., Ma, H., Walker, T.~T.,
  Li, J., Atzmon, D., Cohen, L., Kumar, T. K.~S., Bart{\'{a}}k, R., and
  Boyarski, E. (2019).
\newblock Multi-agent pathfinding: Definitions, variants, and benchmarks.
\newblock In
% Surynek, P. and Yeoh, W., editors,
{\em 12th International Symposium on Combinatorial Search},
pages 151--159. {AAAI} Press.

\bibitem[Surynek, 2019]{DBLP:conf/ijcai/Surynek19}
Surynek, P. (2019).
\newblock Unifying search-based and compilation-based approaches to multi-agent path finding through satisfiability modulo theories.
\newblock In
% Kraus, S., editor,
{\em 28th International Joint Conference on Artificial Intelligence},
pages 1177--1183. ijcai.org.

\bibitem[Svancara and Bart{\'{a}}k, 2019]{DBLP:conf/icaart/SvancaraB19}
Svancara, J. and Bart{\'{a}}k, R. (2019).
\newblock Combining strengths of optimal multi-agent path finding algorithms.
\newblock In
% Rocha, A.~P., Steels, L., and van~den Herik, H.~J., editors,
{\em 11th International Conference on Agents and Artificial Intelligence},
pages 226--231.
SciTePress.

\bibitem[Yu and LaValle, 2013]{NP-hard2}
Yu, J. and LaValle, S.~M. (2013).
\newblock Structure and intractability of optimal multi-robot path planning on graphs.
\newblock In {\em 27th {AAAI} Conference on Artificial Intelligence}.

\end{thebibliography}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
